% !TeX spellcheck = en_US
This will answer a question from the remark in chapter 1, but this maybe takes a while, because we need some category theory first. So lets get started with a few things from \cite[p.~4]{Harder} and \cite{MacLane}.
\section{Category Theory basics}
\begin{definition}[category]
	blabla
\end{definition}
\begin{example}
	a few simple examples
\end{example}
\begin{definition}[functor]
	do it
\end{definition}
Okay i assume a few definitions are clear already, like Category, Functor and some basic Categories like $\Pos, \Ab, \Vect_K, \Groups$, etc.
We need $\Ens$ now, which is the category of all sets and functions within a (variable) set $V$.
\subsection{Products, Projective Limits and Direct Limits in a Category}
\subsubsection{Projective Limit}
I need a category $\CC$ and an ordered set $(I,\le)$, then we can build something nice.
\begin{example}
	\proplbl{exm_order_set_cat}
	We claim that $\EE =(I,\le)$ is a category.
\end{example}
\begin{proof}[\propref{exm_order_set_cat}]
	To show that $\EE$ is a category, we need to check:
	\begin{enumerate}
		\item need $\Ob(\EE)$
		\item need $\Morph(\EE)$
		\item check compositions of $\EE$.
	\end{enumerate}
	then $\EE$ is a category (actual it is a (directed) $\Pos$ category?).
\end{proof}
Then we can start to build something towards the projective limit. ;) Lets collect a few things here
\begin{itemize}
	\item ...
\end{itemize}
\subsection{What is a Presheaf?}
Take a topological space $X$ and define a category $\Open(X)$ of open sets. Name the sets $U,V \subset X$ and define the following morphism
\begin{align*}
	\Hom_{\Open(X)}(U,V) = \begin{cases}
		\emptyset &\quad V \not\subset U\\
		\set{i} &\quad i \text{ inclusion if } V \subset U.
	\end{cases}
\end{align*}
Then we are ready to define the presheaf.
\begin{definition}[Presheaf]
	A \begriff{presheaf} on $X$ with values in a category $\CC$ is a contravariant function from $\Open(X)$ with values in the category $\CC$.
\end{definition}